The Effects of weather on maize yield: New evidence from Kenya

### 2018-12-24 writing/draft3/draft18.tex
working

Besides total cumulative seasonal precipitation and average temperature, CV of both temperature and precipitation and the length and number of dry spells turned out to be significant (see the first column of table~\ref{MainEst}). The relationship of maize yield and each of these variables is linear as is apparent from the figures~\ref{MarEff2}(a) and \ref{MarEff2}(b) in the appendix. In accordance with our expectation, the yield decreases with increasing CV of precipitation. \hl{However, the result for CV of temperature is a bit peculiar as the yield seem to increase with increasing variability of temperature. This is probably because...}
As it is apparent from figures~\ref{MarEff3}(a) and \ref{MarEff3}(b) in the appendix, yield declines with increasing number of dry spells and with length of maximum dry spell linearly. This is in accordance with our expectations.

According to both magnitude of the standardised coefficients and F-values in the first two columns of table~\ref{MainEst}, the most important variable of the model for all counties is average seasonal temperature. Average seasonal temperature has the lowest p-value of the predictors in this model and based on its magnitude and F-value it is much  more important than the second most important variable, which is precipitation.

We will now discuss and compare the results of the models for the subsamples of the ASAL counties (the third and fourth columns of table~\ref{MainEst}) and the non-ASAL counties (the third and fourth columns of table~\ref{MainEst}).

>>>>

Besides cumulative seasonal precipitation and average temperature, CV of both temperature and precipitation and also length and number of dry spells were significant (see the first column of table~\ref{MainEst}). As it is apparent from figures~\ref{MarEff2}(a) and \ref{MarEff2}(b) in the appendix, the relationship of maize yield and each of these variables is linear. In accordance with our expectation, the yield decreases with increasing CV of precipitation. \hl{However, we obtained a peculiar result for CV of temperature as the yield seem to increase with increasing variability of temperature. This is probably because...}

As we can see in figures~\ref{MarEff3}(a) and \ref{MarEff3}(b) in the appendix, yield declines with increasing number of dry spells and with length of maximum dry spell linearly. This is in accordance with our expectations.

According to both magnitude of the standardised coefficients and F-values in the first two columns of table~\ref{MainEst}, the most important variable of the model for all counties is average seasonal temperature. The temperature appears to be much more important than the second most important variable in this model which is cumulative precipitation. The value of the F-statistic corresponding to temperature is $12.010$ while the F-statistic of the linear term of cumulative precipitation is equal to $5.358$ and the F-statistic of its quadratic term is $4.263$. Also, according to its lowest p-value ($6\times10^{-4}$), temperature is the most important covariate.

We will now discuss and compare the results of the models for the subsamples of the ASAL counties (the third and fourth columns of table~\ref{MainEst}) and the non-ASAL counties (the fifth and sixth columns of table~\ref{MainEst}).
